---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
1.Load the data
```{r}
data <- read.csv(unzip("activity.zip"),stringsAsFactors = F)
data0 <- data[!is.na(data$steps),]
```


## What is mean total number of steps taken per day?
1.Calculate the total number of steps taken per day
```{r}
data1 <- with(data0,tapply(steps,date,sum))
```

2.Make a histogram of the total number of steps taken each day
```{r echo=TRUE}
hist(data1,xlab="total number of steps per day")
```


3.Calculate and report the mean and median of the total number of steps taken per day
```{r echo=TRUE}
summary(data1)
```

## What is the average daily activity pattern?

1.Make a time series plot (i.e. \color{red}{\verb|type = "l"|}type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r echo=TRUE}
library(dplyr)
data11 <- group_by(data,interval)
data12 <- summarize(data11,avesteps=mean(steps,na.rm=T))
plot(data12$interval,data12$avesteps,type="l",xlab="interval",ylab="average")
```

2.Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r echo=TRUE}
data12[which.max(data12$avesteps),]$interval
```



## Imputing missing values
1.Calculate and report the total number of missing values in the dataset
```{r echo=TRUE}
nrow(data[is.na(data),])
```


3.Create a new dataset that is equal to the original dataset but with the missing data filled in

I decided to replace missing data with the mean for that 5 minutes interval.
```{r}
ndata <- data
n <- nrow(ndata)
for(i in 1:n){
  if(is.na(ndata[i,]$steps)){
    ndata[i,]$steps <- data12[data12$interval==ndata[i,]$interval,]$avesteps
  }
}

```

4.Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. 
```{r echo=TRUE}
data4 <- with(ndata,tapply(steps,date,sum))
hist(data4,xlab="total number of steps per day",main="Histogram with missing data filled in")
summary(data4)
```

I can say the impuct of imputing missing data is very small.
Mean isn't different from one after missing data filled in.
Median increased slightly.
This result is because I replace missing data with the mean for the interval.

## Are there differences in activity patterns between weekdays and weekends?

1.Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
```{r}
weekdays <- weekdays(as.Date(ndata$date,"%Y-%m-%d"))
##translate Japanese into English
weekdays <- gsub("月曜日","weekday",weekdays)
weekdays <- gsub("火曜日","weekday",weekdays)
weekdays <- gsub("水曜日","weekday",weekdays)
weekdays <- gsub("木曜日","weekday",weekdays)
weekdays <- gsub("金曜日","weekday",weekdays)
weekdays <- gsub("土曜日","weekend",weekdays)
weekdays <- gsub("日曜日","weekend",weekdays)
ndata$weekdays <- weekdays

```

2.Make a panel plot containing a time series plot (i.e. \color{red}{\verb|type = "l"|}type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). See the README file in the GitHub repository to see an example of what this plot should look like using simulated data.

```{r echo=TRUE}
library(ggplot2)
ndata1 <- group_by(ndata,weekdays,interval)
ndata2 <- summarize(ndata1,avesteps=mean(steps))
g <- ggplot(ndata2,aes(interval,avesteps))
g + geom_line() +
  facet_wrap(~weekdays,ncol=1)
```





